%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\cventry
{Senior Site Reliability Engineer} % Job title
{Shine} % Organization
{Remote} % Location
{2023 - now} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I joined as the infrastructure team was being formed. Now a team of 3, we manage Shine's entire infrastructure. My tasks range from minor adjustments and major projects like implementing GCP hosting with Terraform to developing custom Terraform modules for developers. We heavily use tools such as Terraform, GCP, Elasticsearch, and Grafana.}
\item {My responsibilities cover:}
\item {Managing Shine’s entire infrastructure in GCP, including containers (serverless), instances (MIG), queues, databases, and load-balancers.}
\item {Transitioning infrastructure management from nothing to Terraform, by providing several repositories in a self-service mode and with helpful and tailored modules.}
\item {Automating processes via GitHub Actions.}
\item {Setting up monitoring with Grafana (in Terraform): managing logs, metrics, and dashboards.}
\end{cvitems}
}

%------------------------------------------------

%------------------------------------------------

\cventry
{Site Reliability Engineer} % Job title
{Alma} % Organization
{Remote} % Location
{2021 - 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I was the first Site Reliability Engineer when the Platform team was established. We have been up to a 12-person team managing infrastructure (primarily cloud-based), security, data, and developer experience.}
\item {Our work centers around using Terraform, GCP, CloudFlare, Datadog, and Python.}
\item {Responsible for managing Alma's entire infrastructure on GCP, including containers (K8S and serverless), queues, databases, and load balancers.}
\item {Transitioned from using Python scripts to Terraform for infrastructure resource management.}
\item {Focused on security and compliance, including system hardening, isolation, and implementing various mTLS setups with internal Certificate Authorities (CAs).}
\item {Developed Python scripts.}
\item {Automated processes through GitHub Actions.}
\item {Implemented and managed monitoring with Datadog (in Terraform), including logs, metrics, and dashboards.}
\item {Provided Level 2 on-call support.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{DataOps} % Job title
{PeopleDoc} % Organization
{Remote} % Location
{2019 - 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I was the first member of a three-person team tasked with bridging the gap between DBA, SRE, and BI teams.}
\item {Our work primarily utilized Ansible, Airflow, and Python.}
\item {Managed the BI servers, consisting of batch processing systems, Airflow, and Looker servers (approximately 150 servers).}
\item {Developed Python scripts for batch processing (data exports/imports), Airflow plugins, and API interactions.}
\item {Created Debian and Python packages.}
\item {Initiated the development of the first internal data warehouse.}
\item {Provided technical support for BI analysts and data engineers' tools.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Site Reliability Engineer} % Job title
{PeopleDoc} % Organization
{Remote} % Location
{2018 - 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I was part of a five-person team responsible for managing the entire PeopleDoc infrastructure, which included web, DNS, cache, queues, and filer systems, encompassing approximately 1,000 servers across 7 availability zones.}
\item {Our tasks were heavily focused on Ansible and OpenStack and required comprehensive knowledge of all PeopleDoc systems to perform efficiently.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Devops} % Job title
{OVH} % Organization
{Roubaix, France} % Location
{2015 - 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {I was part of a team of 5 responsible for the core services at OVH. We inherited an outdated and unmaintained infrastructure, and our goal was to enhance its stability, uniformity, and scalability.}
\item {We also maintained a PCIDSS-ready infrastructure, ensuring it met the highest PCIDSS compliance standards.}
\item {Managed internal information systems, including public web servers, databases, task workers, load balancers, and more, totaling around 1,000 servers.}
\item {Oversaw the PCIDSS-certified information systems for the Private Cloud Computing service.}
\item {Handled the PCIDSS-certified payment system, OVH Secure Payment.}
\item {Managed corporate bastion hosts.}
\item {Migrated outdated and unmaintained services to standardized and hardened platforms.}
\item {Focused on automation, configuration management, and scripting.}
\item {Ensured security and monitoring.}
\item {Provided Level 2 and Level 3 on-call support.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{System Administrator} % Job title
{ISVTEC} % Organization
{Lyon, France} % Location
{2012 - 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed web, email, SQL, and DNS services across 300 client servers.}
\item {Executed seamless migrations of mail and websites with zero downtime.}
\item {Transitioned services to more scalable and fault-tolerant systems.}
\item {Provided Level 1 on-call support.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{System and Network Administrator} % Job title
{ICEDev} % Organization
{Lyon, France} % Location
{2011 - 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed customer services including web hosting, email, and DNS on company servers.}
\item {Handled network and firewall management.}
\item {Performed migrations of websites and email services.}
\item {Conducted data center operations.}
\item {Provided helpdesk support.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{IT Consultant} % Job title
{Astek} % Organization
{Lyon, France} % Location
{2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintenance, repair, and operation of various Unix systems}
\end{cvitems}
}

%------------------------------------------------

\cventry
{System and Database Administrator} % Job title
{Acteos} % Organization
{Roubaix, France} % Location
{2007 - 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed internal infrastructure, including Oracle databases and Oracle AS, across 70 servers.}
\item {Conducted on-premise installations and migrations of Acteos products.}
\item {Provided Level 3 support for systems and databases.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
